---
title: "P8105_hw1_ms8626"
author: Meredith Steinberg
date: 2024-09-12
output: github_document
  
---
# Problem 1
### load libraries
```{r}
library(palmerpenguins)
library(tidyverse)
```

### load penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

### penguins dataset includes 344 rows and 8 columns (variables) describing penguins including species, island, bill length, bill depth, flipper length, body mass, sex, and year
```{r}
ncol(penguins)
nrow(penguins)
```

### taking mean flipper length
```{r}
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
### mean flipper length is 200.9152mm

```{r yx_scatter}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()
ggsave("scatterplot.pdf")
```

# Problem 2

### creating dataframe 
```{r}
dataframe_pb2=
  tibble(
    variable1 = rnorm(10), 
    variable2 = variable1>0,
    variable3 = c("My", "name", "is", "Meredith", "and", "I", "like", "flowers", "very", "much"),
    variable4 = factor(c("yes", "no", "maybe", "yes","yes", "no", "maybe", "yes", "maybe", "yes"))
  )
```

### taking means of variables
```{r}
mean(pull(dataframe_pb2, variable1), na.rm = TRUE)
mean(pull(dataframe_pb2, variable2), na.rm = TRUE)
mean(pull(dataframe_pb2, variable3), na.rm = TRUE)
mean(pull(dataframe_pb2, variable4), na.rm = TRUE)
```
### taking mean of variables 1 and 2 works, but not for 3 and 4

```{r, eval=FALSE}
as.numeric(pull(dataframe_pb2, variable2), na.rm = TRUE)
as.numeric(pull(dataframe_pb2, variable3), na.rm = TRUE)
as.numeric(pull(dataframe_pb2, variable4), na.rm = TRUE)
```
### variables 2 and 4 are being converted to a numeric class, where variable 2 is a binary variable and variable 4 has 3 different factor "levels"
### variable 3 cannot be converted to a numeric class which makes sense why we can't take the mean of characters that are all unique


